Feature importance analysis

### 2020-04-18 analysis/feature-importance.Rmd
wflow_publish(knitr_in("analysis/feature-importance.Rmd"), view = FALSE,     verbose = TRUE)

```{r feature-importance-1 }
fi_ranked_hr <- fi_permut_hr_buffer2$res %>%
  tibble::rownames_to_column("measure") %>%
  tidyr::pivot_longer(
    cols = starts_with("B"),
    values_to = "importance", names_to = "feature"
  ) %>%
  mutate(wavelength = seq(420, 995, 4.75)) %>%
  mutate(numeric_id = seq(5, 126, 1)) %>%
  arrange(desc(importance)) %>%
  mutate(rank = row_number()) %>%
  select(-measure)
fi_ranked_hr

fi_ranked_vi <- fi_permut_vi_buffer2$res %>%
  tibble::rownames_to_column("measure") %>%
  tidyr::pivot_longer(
    cols = starts_with("B"),
    values_to = "importance", names_to = "feature"
  ) %>%
  # mutate(wavelength = seq(420, 995, 4.75)) %>%
  arrange(desc(importance)) %>%
  mutate(rank = row_number()) %>%
  select(-measure) %>%
  mutate(feature = stringr::str_replace(feature, "bf2_", ""))
fi_ranked_vi
```

@@

df_wavelengths_from_indices_label <- df_wavelengths_from_indices_imp %>%
  arrange(rank) %>%
  group_by(class, rank) %>%
  dplyr::slice(1) %>%
  ungroup() %>%
  arrange(rank) %>%
  slice(1:10)

df_wavelengths_from_hr <- data_hr_merged %>%
  arrange(rank) %>%
  group_by(class, rank) %>%
  dplyr::slice(1) %>%
  ungroup() %>%
  arrange(rank) %>%
  slice(1:10) %>%
  select(-class) %>%
  rename(class = feature)

@@

```{r fi-hr-ale, dev = c("png", "pdf")}
fi_ale_hr_buffer2$plot(
  features = df_wavelengths_from_hr$class,
  ncol = 2
)
```

@@

```{r}
fi_ale_hr_buffer2_gs20$plot(
  features = df_wavelengths_from_hr$class,
  ncol = 2
)
```

@@

```{r fi-vi-ale, dev = c("png", "pdf")}
fi_ale_vi_buffer2$plot(
  features = paste0("bf2_", df_wavelengths_from_indices_label$class),
  ncol = 2
)
```

@@

```{r}
fi_ale_vi_buffer2_gs20$plot(
  features = paste0("bf2_", df_wavelengths_from_indices_label$class),
  ncol = 2
)
```

>>>>

```{r feature-importance-1 }
fi_ranked_hr <- fi_permut_hr_buffer2$res %>%
  tibble::rownames_to_column("measure") %>%
  tidyr::pivot_longer(
    cols = starts_with("B"),
    values_to = "importance", names_to = "feature"
  ) %>%
  dplyr::mutate(wavelength = seq(420, 995, 4.75)) %>%
  dplyr::mutate(numeric_id = seq(5, 126, 1)) %>%
  dplyr::arrange(desc(importance)) %>%
  dplyr::mutate(rank = row_number()) %>%
  dplyr::select(-measure)
fi_ranked_hr

fi_ranked_vi <- fi_permut_vi_buffer2$res %>%
  tibble::rownames_to_column("measure") %>%
  tidyr::pivot_longer(
    cols = starts_with("B"),
    values_to = "importance", names_to = "feature"
  ) %>%
  # mutate(wavelength = seq(420, 995, 4.75)) %>%
  dplyr::arrange(desc(importance)) %>%
  dplyr::mutate(rank = row_number()) %>%
  dplyr::select(-measure) %>%
  dplyr::mutate(feature = stringr::str_replace(feature, "bf2_", ""))
fi_ranked_vi
```

@@

df_wavelengths_from_indices_label <- df_wavelengths_from_indices_imp %>%
  arrange(rank) %>%
  group_by(class, rank) %>%
  dplyr::slice(1) %>%
  dplyr::ungroup() %>%
  dplyr::arrange(rank) %>%
  dplyr::slice(1:10)

df_wavelengths_from_hr <- data_hr_merged %>%
  arrange(rank) %>%
  group_by(class, rank) %>%
  dplyr::slice(1) %>%
  dplyr::ungroup() %>%
  dplyr::arrange(rank) %>%
  dplyr::slice(1:10) %>%
  dplyr::select(-class) %>%
  dplyr::rename(class = feature)

@@

```{r fi-hr-ale, dev = c("png", "pdf")}
fi_ale_hr_buffer2$plot(
  features = df_wavelengths_from_hr$class,
  ncol = 2
) +
  theme_pubr(base_size = 14) +
  theme(
    legend.text = element_text(size = 13),
    legend.title = element_text(size = 13)
  )
```

@@

```{r}
fi_ale_hr_buffer2_gs20$plot(
  features = df_wavelengths_from_hr$class,
  ncol = 2
) +
  theme_pubr(base_size = 14) +
  theme(
    legend.text = element_text(size = 13),
    legend.title = element_text(size = 13)
  )
```

@@

```{r fi-vi-ale, dev = c("png", "pdf")}
fi_ale_vi_buffer2$plot(
  features = paste0("bf2_", df_wavelengths_from_indices_label$class),
  ncol = 2
) +
  theme_pubr(base_size = 14) +
  theme(
    legend.text = element_text(size = 13),
    legend.title = element_text(size = 13)
  )
```

@@

```{r}
fi_ale_vi_buffer2_gs20$plot(
  features = paste0("bf2_", df_wavelengths_from_indices_label$class),
  ncol = 2
) +
  theme_pubr(base_size = 14) +
  theme(
    legend.text = element_text(size = 13),
    legend.title = element_text(size = 13)
  )
```
